How to make a delicious pizza

### 2012-12-19 article.tex

\documentclass[a4paper,12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{fullpage,url}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{color}

\title{How to make a delicious pizza}
\author{Yuto Takei \\ The University of Tokyo}

@@

* Why do we limit to integer space?

@@

$ <num> ::= ... | -2 | -1 | 0 | 1 | 2 | ... $ .
$ <var> ::= x | y | ... $
$ <term> ::= <num> \cdot <var> $
$ <expr> ::=  <term> + <term> + \cdots + <num> >= 0 $
$ <la> ::= <expr>
         | <la> \wedge <la> $
$ <pvar> ::= A | B | ... $
$ <pred> ::= <pvar> ( <var>, <var>, ... ) $
$ <hornTerm> ::= <pvar> | <pred> $
$ <horn> ::= <hornTerm> \wedge <hornTerm> \wedge \cdots \longrightarrow
         <hornTerm> $

@@

Def <Implication Tree>:

@@

$ <la> ::= <expr>
         | <la> \wedge <la>
         | <la> \vee <la> $

@@

\section{Experiment}
\section{Future Work}
\section{Conclusion}

>>>>

\documentclass{llncs}

\usepackage{fullpage,url}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}
\usepackage{syntax}

\title{How to make a delicious pizza}
\author{Yuto Takei}
\institute{The University of Tokyo}

@@

Discussion on Real space

@@

\setlength{\grammarparsep}{-2pt}
\setlength{\grammarindent}{6em}
\begin{grammar}

<num> ::= All integers

<var> ::= Arithmetic variables

<term> ::= $<num> \cdot <var>$

<expr> ::=  $<term> + <term> + \cdots + <num> \leq 0$

<la> ::= $<expr>$ | $<la> \wedge <la>$

<pvar> ::= Predicate variables

<pred> ::= $<pvar> ( <var>, <var>, ... )$

<hTerm> ::= <la> | <pred>

<horn> ::= $<hTerm> \wedge <hTerm> \wedge \cdots \longrightarrow <hTerm>$

\end{grammar}

@@

Def <Resolution Tree>:

@@

\setlength{\grammarindent}{2em}
\begin{grammar}
<la> ::= <expr> | $<la> \wedge <la>$ | $<la> \vee <la>$
\end{grammar}

@@

\section{Completeness and Complexity}

\section{Experiment}

We limited to integer space

\section{Future Work}
\section{Conclusion}
